The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-16 paper/ms.tex
timothy van reeth as coauthor

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6,7}$
Timothy R. White,$^{5,8}$\newauthor
Daniel Huber,$^{9,10,11}$
Ashley Chontos,$^{9}$
Victor Silva Aguirre,$^{5}$
Victoria Antoci,$^{5}$\newauthor
Suzanne Aigrain,$^{3}$ 
Timothy R. Bedding,$^{10,5}$
Jie Yu,$^{10,5}$ 
Amalie Stokholm,$^{5}$\newauthor
and friends
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA\\
$^{8}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{9}$Institute for Astronomy, University of Hawai‘i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{10}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{11}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA
}

@@

From the HR diagram, we identify 64 of these objects as evolved systems, and the remaining~38 lie on the main sequence. One of the main sequence objects, BD+43~3068 is a G0 dwarf with a $G$ magnitude of 8.267944 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a Solar analogue: it is possible that it was previously misidentified as a giant. Regrettably, it is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star.

@@

\subsection{Main Sequence Pulsators}
\label{pulsators}

@@

\subsection{Eclipsing Binaries}
\label{ebs}

>>>>

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6,7}$
Timothy R. White,$^{5,8}$\newauthor
Daniel Huber,$^{9,10,11}$
Ashley Chontos,$^{9}$
Victor Silva Aguirre,$^{5}$
Victoria Antoci,$^{5}$\newauthor
Suzanne Aigrain,$^{3}$ 
Timothy R. Bedding,$^{10,5}$
Jie Yu,$^{10,5}$ 
Amalie Stokholm,$^{5}$\newauthor
Timothy van Reeth,$^{5,10}$
and friends
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA\\
$^{8}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{9}$Institute for Astronomy, University of Hawai‘i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{10}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{11}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA
}

@@

We identify the evolutionary state of objects in the main sequence versus evolved stars first from the \gaia colour-magnitude diagram in Figure~\ref{hrdiagram}. Taking a cutoff in \gaia $Bp-Rp < 1$, we identify 64 of these objects as evolved systems, and the remaining~38 lie apparently on the main sequence.

One of the main sequence objects, BD+43~3068 is a G0 dwarf with a $G$ magnitude of 8.267944 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a Solar analogue: it is possible that it was previously misidentified as a giant. Regrettably, it is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star. This light curve shows neither rotational modulation (as determined by its featureless autocorrelation) nor evidence of transits.

Considering objects lying photometrically on the main sequence, from the \kepler power spectrum we identify solar-like oscillations in HD~182354 and HD~176209 at frequencies consistent with them being subgiants. \textcolor{red}{Get frequencies}.

@@

\subsection{Main Sequence Stars}
\label{mainseq}

\subsubsection{Classical Pulsators}
\label{pulsators}

@@

\subsubsection{Eclipsing Binaries}
\label{ebs}
